---
title: "Getting Started with binomial"
author: "Ana Fung"
date: "May 1, 2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
library(binomial)
```

## Introduction to the binomial package

The package `"binomial"` implements functions for calculating probabilities of a Binomial random variable, and related calculations such as the probability distribution, the expected value, variance, etc.

## `bin_choose()` function

When you have a number of trials and successes in mind, you can invoke the `bin_choose()` function to calculate the number of
combinations in which k successes can occur in n trials.

```{r}
bin_choose(trials = 5L, success = 2)
```

The argument `trials = ` only accepts integers; if the input is not an integer/not specified with suffix "L", there will be an error. Additionally, the number of successes cannot be greater than the number of trials. 

## `bin_probability()` function

To calculate the probability of getting a certain number of successes in a number of trials, use this function. 

```{r}
#assuming that the probability of success is 0.5
bin_probability(success = 0:2, trials = 5L, prob = 0.5)
```

Like `bin_choose()`, the `trials = ` input should be specified as an integer using the suffix "L", or else the function will return an error. The `prob =` argument should contain an input that is within the valid range of a probability (between 0 and 1), and the number of successes should not be greater than the number of trials; if the `success = ` argument contains an input with length greater than 1, all of its elements need to be less than or equal to the number of trials.

## `bin_distribution()` function

To generate a data frame that shows the prbability distribution of every possible number of successes within a certain number of trials, use this function.

```{r}
# binomial probability distribution
bin_distribution(trials = 5L, prob = 0.5)
```

Keep in mind that the rules about the argument inputs still apply.

## plotting a probability histogram

To plot a probability histogram of the binomial distribution object generated by `bin_distribution()`, use the method exemplified here (keeping in mind the rules about the argument inputs):

```{r}
dis1 <- bin_distribution(trials = 5L, prob = 0.5)
plot(dis1)
```

## `bin_cumulative()` function

To generate another data frame that displays the cumulative probabilities of success, use this function. 
```{r}
# binomial cumulative distribution
bin_cumulative(trials = 5L, prob = 0.5)
```

This function should return a data frame with both the probability distribution and the cumulative probabilities: sucesses in the first column, probability in the second column, and cumulative in the third column.

## plotting a cumulative distribution object

To plot the cumulative distribution object generated by `bin_cumulative()`, use the following method(keeping in mind the rules about the argument inputs):

```{r}
# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5L, prob = 0.5)
plot(dis2)
```

## `bin_variable()` function

To see a printed list of your input variables and their values, use this function/method. 

```{r}
bin_variable(5L, 0.3)
```

## summary of the binomial variable

To get a full summary description of a binomial variable object, use this following method.

```{r}
bin1 <- bin_variable(trials = 10L, p = 0.3)
binsum1 <- summary(bin1)
binsum1
```

In other words, assign `bin_variable()` to an object so that it inherits the attributes of the function, and then pass the object to `summary()`.

## functions of measures

The `"binomial"` package includes a few functions of measures, i.e. functions that calculate the mean, variance, mode, skewness, and tailedness of a binomial distribution; each function takes the arguments `trials` and `prob`.

```{r}
#mean of the distribution
bin_mean(10L, 0.3)
#variance of the distribution
bin_variance(10L, 0.3)
#mode of the distribution
bin_mode(10L, 0.3)
#skewness of the distribution
bin_skewness(10L, 0.3)
#tailedness of the distribution via the Kurtosis formula
bin_kurtosis(10L, 0.3)
```





